Data paper

### 2015-02-15 papers/data_paper/datapaper.tex
monday

(e.g.~\citealt{dressler1989,yee1992,kormendyrichstone1995,magorrian1998,ferraresemerritt2000,gebhardt2000,graham2001,
marconihunt2003,haringrix2004,graham2012bent}). {\bf AL: need to talk to you about Laor's work}\\
The tightness (or small scatter) of the observed black hole mass correlations has led to the idea

@@

the driving mechanisms of the black hole - galaxy coevolution.

@@

to the $z=0$ black hole mass - galaxy mass relation.
Scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct

@@

Many accurate $M_{\rm BH}$ predictions would help derive 

@@

and space density (\citealt{grahamdriver2007smbhmassdensity} and references therein; \citealt{comastri2015}). \\
Since the first stellar dynamical detections of black holes were carried out in the '80s 
(see the references in the reviews by \citealt{kormendyrichstone1995} and \citealt{richstone1998}), 

@@

and it has recently become a statistically meaningful sample -- of the order of 100 objects -- 

@@

The knowledge that many elliptical galaxies contain embedded stellar disks can be dated back to 
at least three decades ago 

@@

After examining long-slit spectroscopic observations of morphologically classified elliptical galaxies in the Fornax cluster, 
\cite{donofrio1995} and \cite{graham1998fornax} concluded that only $\sim$$1/3$ of their galaxies do not harbour any disk-like component.
Surveys with integral field spectrographs of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
have further changed our idea of ``elliptical'' galaxies, 
being all but simple and featureless pressure-supported systems.

@@

\cite{krajnovic2013} showed that ``fast rotators'' as a class are simply disks or at least disk-like objects. 

@@

Given the prevalence of disks, it is important to perform bulge/disk decompositions, 
if one is to properly explore the black hole-bulge connection. \\

@@

Galaxy decomposition is a parametric analysis that allows one to fit the surface brightness distribution

@@

With the two-dimensional (2D) technique one fits analytic functions directly to digital images. \\

@@

Interestingly, the past studies all %investigated the black hole mass scaling relations using 
used almost the same sample of galaxies, 
but they claimed some contradictory conclusions.
One study \citep{grahamdriver2007} obtained a good $M_{\rm BH}-n_{\rm sph}$ correlation
(the bulge S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars), 

@@

\cite{lasker2014anal} declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity and the bulge luminosity, 

@@

We will use these to obtain improved black hole mass scaling relations using the largest to date sample of 72 galaxies.

This paper is structured as follows.
Section \ref{sec:data} presents the data-set used to conduct this study. 
Section \ref{sec:anal} describes how we performed the galaxy decompositions, 
i.e.~how we identified and modeled the sub-components that constitute our galaxies. 
In Section \ref{sec:res} we outline the results from our analysis 
and we discuss the error analysis. 
Section \ref{sec:concl} summarizes our main conclusions. 
The individual galaxy decompositions are made available in the electronic version of this manuscript.

\section{Data}
\label{sec:data}
%\subsection{Initial sample}
Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
has been reported in the literature and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC observation was made publicy 
available at the time we began our investigation (2013).
Black hole masses were drawn from the catalog of \citet{grahamscott2013} for 70 galaxies,
from \citet{rusli2013bhmassesDM} for 4 galaxies 
and from \citet{greenhill2003} for 1 galaxy.

@@

\subsection{\emph{Spitzer}/IRAC observations}
\subsubsection{Data acquisition}
For each of our 75 galaxies, we downloaded from the 
Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs), 
listed in Table \ref{tab:obs}.
Each AOR is an individual Spitzer observation sequence, and
includes a number of data frames (the individual exposures) and the calibration data.
The data frames were selected to be %``enhanced Level 1 products'', or
corrected Basic Calibrated Data (cBCD).
Basic Calibrated Data (BCD) are produced by the IRAC Level 1 pipeline. 
This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
BCD frames are further processed through an ``artifact correction'' pipeline 
that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
It looks like a decaying trail of pixels, repeating every fourth column.
Column pulldown is caused by a bright pixel that triggers a bias shift within its respective column, 
creating a lower background value throughout the entire column than in the surrounding columns.}.
After the artifact correction has been applied, the BCD becomes a cBCD.

\subsubsection{Mosaicing}
We performed image mosaicing using the %(command line version of the) 
MOPEX package \citep{makovozmarleau2005mopex}.
Individual cBCD frames with exposure time of $1~\rm sec$ were rejected.
Permanent or semi-permanent bad pixels, contained in a semi-static mask (the ``pmask''), were ignored.
Each AOR is associated to a specific pmask. 
Therefore, when multiple AORs were available for the same galaxy, 
we merged the different pmasks. 
Outlier rejection was performed with the dual outlier and multi-frame techniques.
The pixel size of the mosaic was set to be the same as the input cBCD frames ($1''.22 \times 1''.22$).
For $3.6~\rm \mu m$ observations with this pixel scale, 
the photometric zeropoint magnitude is $m_{\rm zp} = 17.26 \rm~mag$.
The orientation of the mosaic was set to the average rotation angle of the input cBCD frames. 
%{\bf TBD: not n-e oriented or re-sampled because problems with 2d PSF. }
Individual cBCD frames were combined together into a single mosaic with the default linear interpolation algorithm.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/m49nooverlap.eps}
\includegraphics[width=0.49\columnwidth]{images/m49overlap.eps}
\caption{An example of the \emph{overlap} correction. 
The image mosaic of the galaxy M49 was obtained by co-adding frames coming from 8 different AORs.
The evident patchiness (left image) was removed (right image) using the \emph{overlap} module.}
\label{fig:overlap}
\end{center}
\end{figure}

@@

\subsubsection{Additional aestethic corrections}
The image mosaics of 4 galaxies (NGC 0821, NGC 2974, NGC 4291, NGC 4459) were found to be affected 
by bright, highly saturated stars lying close to the target galaxies.
These stars were modeled and subtracted using the software Galfit \citep{peng2010} 
and the extended IRAC Point Response Function (PRF) image at $3.6~\rm \mu m$.
This helped remove the extended wings and spikes of the saturated stars 
(see Figure \ref{fig:aesth} for an example).

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n4459brightstar.eps}
\includegraphics[width=0.49\columnwidth]{images/n4459nobrightstar.eps}
\caption{An example of aestethic correction.
The images show the mosaic of the galaxy NGC 4459 before (left) and after (right) the removal 
of a bright saturated star.}
\label{fig:aesth}
\end{center}
\end{figure}

\subsubsection{Image masking}
Galactic stars and any other objects different from the target galaxy 
were masked through a two-step procedure.
First, we created an initial mask using the IRAF task 
{\tt objmasks}, %\footnote{{\tt objmasks} is part of the {\tt noao.nproto} package.},
that identifies objects by threshold sigma detection.
Then, we refined each mask by hand, using the software 
SAOImage DS9\footnote{SAOImage DS9 development has been made possible by funding 
from the Chandra X-ray Science Center (CXC) 
and the High Energy Astrophysics Science Archive Center (HEASARC).} 
in conjunction with the IRAF task 
{\tt mskregions}. %\footnote{{\tt mskregions} is part of the {\tt proto} package.}.
We identified and carefully masked not only contaminating sources located in the field of the image mosaic,
but also objects overlapping with the target galaxy, such as foreground stars, globular clusters or red giant stars.

\subsubsection{1D PSF}
The one-dimensional Point Spread Function was charachterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected galaxy radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
%We employed both a Gaussian and a Moffat \citep{moffat1969} profile. 
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained %$FWHM = 2''.03$ for the Gaussian function,
$(\alpha, \beta) = (2''.38, 4.39)$ %for the Moffat function
(see Appendix \ref{sec:app1} for the analytical expressions of the Moffat function).

\subsubsection{2D PSF}
The IRAC support team provides the users with a two-dimensional instrument Point Response Function (PRF) at $3.6~\rm \mu m$.
However, we found this PRF to be inadequate for the purposes of our analysis.
In fact, the $FWHM$ of the IRAC instrument PRF ($\sim 1''.8$), as measured by the IRAF task {\tt imexamine}, 
is systematically smaller than the average $FWHM$ of ``real'' stars ($\sim 2''.0$). 
Figure \ref{fig:psf} illustrates this issue.
We also tested the IRAC PRF by providing it as the input Point Spread Function (PSF) for Galfit 
and fitting a number of stars in different image mosaics.
A visual inspection of the fit residuals confirmed that the IRAC instrument PRF is narrower than ``real'' point sources.
For this reason, we constructed our 2D PSF according to the following method 
(as directed by C. Peng, private communication).\\
We provided the IRAC instrument PRF as the input PSF for Galfit 
and simultaneously fit 7 bright stars (belonging to different mosaics), 
modeling the stars with Moffat profiles 
and constraining all the profiles to have the same $(\alpha, \beta)$, position angle and axis ratio.
The 2D PSF image was then obtained by taking the best fit Moffat model -- the same best-fit model for all 7 stars, by construction -- 
and convolving it with the IRAC instrument PRF.
The advantage of this method is to obtain a 2D PSF that is wider than the instrument PRF, 
but maintains the asymmetric features of the instrument PRF (e.g.~wings and spikes).
%This procedure was repeated using a Moffat profile in place of the Gaussian profile.
We then tested this 2D PSF 
on a number of stars (these stars were different from the 7 stars employed to build the 2D PSF image)
and verified that it correctly reproduces the shape of ``real'' point sources.

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth, trim = 220 30 20 20, clip=True]{images/psf.eps}
%\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
%\includegraphics[width=1\columnwidth]{images/PRF_IRACch1_129_129_cut.eps}
\caption{Normalized flux versus radial distance 
from the image centroid of an observed point source (top panel) 
and of the IRAC instrument PRF (bottom panel). 
The normalized flux is given in arbitrary units, 
and the radial distance is in units of pixel size of the IRAC detector (1 pixel = $1''.22$).
The blue solid line shows our 1D Moffat PSF model,
which has been normalized to intersect the data point with the largest flux. 
The $FWHM$ of the IRAC PRF is clearly smaller than that of a ``real'' star.
The inserts display the images of the observed point source and the IRAC PRF.}
\label{fig:psf}
\end{center}
\end{figure}

\subsection{Additional data}
\label{sec:adddata}
\subsubsection{Kinematics}
\label{sec:kinem}
A kinematical classification (slow/fast rotator) is available for 34 of our 75 galaxies 
from the ATLAS$^{\rm 3D}$ survey \citep{atlas3dIII-MNRAS} 
and for 3 additional galaxies from \citet{scott2014}.
This classification (Table \ref{tab:sample}, column 7) 
concerns the kinematic properties of galaxies within the instrument field-of-view, % (typically up to one effective radius),
but does not contain additional information -- crucial for our analysis -- about kinematic substructures, 
such as embedded disks or kinematically decoupled components, 
which can require separate modeling.
For this reason, we also visually inspected the velocity fields of our galaxies, 
when available from the literature.
Velocity maps were taken from the ATLAS$^{\rm 3D}$ survey for 34 galaxies 
(observed with SAURON by \citealt{krajnovic2011}),
from \citet{scott2014} for 2 galaxies 
(observed with WiFeS)
and from the SLUGGS survey for 12 galaxies 
(observed with DEIMOS by \citealt{arnold2014}).
While the field-of-views of SAURON ($33'' \times 41''$) and WiFeS ($25'' \times 38''$) 
reach to about one galaxy effective radius (for our local galaxies),
observations taken with DEIMOS can probe the galaxy kinematics well beyond two effective radii.

\subsubsection{AGNs and nuclear dust}
The X-ray, UV and optical radiation 
emitted by the the accretion disks of Active Galactic Nuclei (AGNs) can stimulate infrared thermal emission 
from circumnuclear dust, if present. 
This means that if a galaxy hosts an optical AGN \emph{and} a certain amount of nuclear dust,
we expected to detect some non-stellar nuclear emission at $3.6~\rm \mu m$.
It is therefore important to identify which of our galaxies have both an optical AGN and circumnuclear dust.
To help with this task, we searched NED\footnote{NED is the NASA/IPAC Extragalactic Database.} 
for the individual galaxies and their associated literature.
Unsurprisingly, dusty AGNs were more frequently found in late-type spiral galaxies.

\subsubsection{S\'ersic/core-S\'ersic classification}
\label{sec:corser}
Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
with partially depleted cores, 
i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs.
The majority are thus unresolved in our image mosaics. 
We masked these unresolved cores by excluding the surface brightness profile 
within 3 PSF's $FWHM$ from the galaxy center.
In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
plus 3 PSF's $FWHM$.
The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
This resulted in us assigning cores to just 2 galaxies when using this alternative method 
if no high resolution image was available.

\section{Analysis}
\label{sec:anal}
\subsection{Isophotal analysis}
We performed an isophotal analysis of our galaxies using the IRAF task {\tt ellipse} \citep{taskellipse}, 
which fits elliptical isophotes to galaxy images.
The center of the isophotes was held fixed, while the ellipticity ($\epsilon$), the position angle ($P.A.$),  
and the amplitude of the fourth harmonic\footnote{The amplitude of the fourth harmonic deviations from perfect ellipses 
($B4$) parameterizes the diskyness ($B4>0$) or boxyness ($B4<0$) of the isophotes.} ($B4$) were allowed to vary with radius.
The step in semi-major axis length between successive ellipses was set to increase linearly, 
and then geometrically in our second run\footnote{In case of linear steps, 
the semi-major axis length for the next ellipse was calculated by adding $1$ pixel to the current length.
In case of geometric steps, the semi-major axis length for the next ellipse 
was calculated as $1.1$ times the current length.}.
As a result, for each galaxy we produced respectively a ``linearly sampled'' and a ``logarithmically sampled'' 
surface brightness profile along the major-axis. 
Major-axis surface brightness profiles were then projected along the equivalent-axis,
i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$), 
also called the circularized radius.
Isophotes corresponding to an intensity less than $3 \times RMS_{\rm sky}$ were rejected.
Some surface brightness profiles were truncated at our discretion before the $3 \times RMS_{\rm sky}$ limit, 
according to specific technical reasons (e.g.~contamination from light of a neighboring galaxy, 
disturbed morphology in the galaxy outskirts, etc.).
Individual cases are discussed in Section \ref{sec:indgal}.

>>>>

(e.g.~\citealt{dressler1989,yee1992,kormendyrichstone1995,laor1997,magorrian1998,ferraresemerritt2000,gebhardt2000,graham2001,
marconihunt2003,haringrix2004,graham2012bent,grahamscott2015}). \\
The tightness of (i.e.~the small scatter about) the observed black hole mass correlations has led to the idea

@@

the driving mechanisms of the black hole -- galaxy coevolution.

@@

to match the $z=0$ black hole mass -- galaxy mass relation.
Such scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct

@@

Moreover, many accurate $M_{\rm BH}$ predictions enable one to derive 

@@

and space density (e.g.~\citealt{grahamdriver2007smbhmassdensity,comastri2015}). 
All of these examples depend on the $z=0$ relations, 
and as such the recalibration of the black hole mass -- bulge stellar mass ratio ($M_{\rm BH}/M_{\rm *,sph}$) in large bulges,
from $0.1 - 0.2\%$ (e.g.~\citealt{haringrix2004}) to $0.36\%$ \citep{graham2012bent} and then $0.49\%$ \citep{grahamscott2015}, 
has many substantial implications. \\
Since the early stellar dynamical detections of black holes were carried out in the '80s 
(see the references in the reviews by \citealt{kormendyrichstone1995}, \citealt{richstone1998} 
and \citealt{graham2015bulges} for pioneering papers), 

@@

and it has recently become a statistically meaningful sample  

@@

The knowledge that many ``elliptical'' galaxies actually contain embedded stellar disks dates back  
at least three decades  

@@

After examining long-slit and integral field unit spectroscopic observations of morphologically classified elliptical galaxies in the Fornax cluster, 
\cite{donofrio1995}, \cite{graham1998fornax} and \cite{scott2014} concluded that only 3 bright galaxies do not harbour a disk-like component.
Larger surveys with integral field spectrographs of early-type galaxies, such as the ATLAS$^{\rm 3D}$ Project \citep{cappellari2011}, 
have further advanced this view of ``elliptical'' galaxies being all but simple and featureless pressure-supported systems.

@@

\cite{krajnovic2013} showed that ``fast rotators'' as a class are disk-galaxies or at least disk-like galaxies. 

@@

Given the prevalence of disks, it is clearly important to perform bulge/disk decompositions, 
if one is to properly explore the black hole-bulge connection. 
Indeed, separating the disk light from that of the bulge has led to the discovery of the missing population of compact, massive spheroids 
in the local Universe {\bf (Graham, Dullo, Savorgnan 2015)}.
If we are to properly understand the evolution of galaxies, we need to understand their components.\\

@@

Such galaxy decomposition involves a parametric analysis that allows one to fit the surface brightness distribution

@@

With the two-dimensional (2D) technique, one fits analytic functions directly to the 2D images. \\

@@

{\bf Rusli has explored the black hole - core relation.}
Interestingly, the past studies used almost the same sample of galaxies, yet they claimed some contradictory conclusions.
For example, one study \citep{grahamdriver2007} obtained a good $M_{\rm BH}-n_{\rm sph}$ correlation
(the bulge S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars, \citealt{trujillo2001}), 

@@

In addition, \cite{lasker2014anal} {\bf who did not work at 3.6um} 
declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity and the bulge luminosity, 

@@

We will use these in a series of forthcoming papers to obtain improved black hole mass scaling relations 
using the largest sample (66) of galaxies to date.

This paper is structured as follows.
Section \ref{sec:data} presents the galaxy sample and imaging data-set used to conduct this study. 
Section \ref{sec:anal} describes how we performed the galaxy decompositions, 
i.e.~how we identified and modeled the sub-components that constitute our galaxies. 
In Section \ref{sec:res} we outline the results from our analysis and discuss the error analysis. 
Section \ref{sec:concl} summarizes our main conclusions. 
The individual galaxy decompositions are made available in the electronic version of this manuscript.

\section{Data}
\label{sec:data}
%\subsection{Initial sample}
Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
had been reported in the literature at the time we started this project, 
and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC\footnote{IRAC is the InfraRed Array Camera onboard the \emph{Spitzer} Space Telescope.} 
observation was publicy available.
Black hole masses were drawn from the catalog of \citet{grahamscott2013} for 70 galaxies,
from \citet{rusli2013bhmassesDM} for 4 galaxies and from \citet{greenhill2003} for 1 galaxy. 
As explained in Section \ref{sec:res}, 
this initial sample was ultimately reduced to 66 galaxies for which useful bulge parameters could be obtained.

@@

\subsection{\emph{Spitzer}/IRAC observations}
\subsubsection{Data acquisition}
For each of our 75 galaxies, we downloaded from the 
Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs), 
listed in Table \ref{tab:obs}.
Each AOR is an individual Spitzer observation sequence, and
includes a number of data frames (the individual exposures) and the calibration data.
The data frames were selected to be %``enhanced Level 1 products'', or
corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
BCD frames are further processed through an ``artifact correction'' pipeline 
that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
It appears as a decaying trail of pixels, repeating every fourth column.
``Column pulldown'' is caused by a bright pixel that triggers a bias shift within its respective column, 
creating a lower background value throughout the entire column than in the surrounding columns.}.
After the artifact correction has been applied, the BCD becomes a cBCD.

\subsubsection{Mosaicking}
We performed image mosaicking using the MOPEX package \citep{makovozmarleau2005mopex}.
This enabled the production of suitably wide-field-of-view images for accurate sky background subtraction.
Individual cBCD frames with exposure time of $1~\rm sec$ were rejected.
Permanent or semi-permanent bad pixels, contained in a semi-static mask (the ``pmask''), were ignored.
Each AOR is associated to a specific pmask. 
Therefore, when multiple AORs were available for the same galaxy, 
we merged the different pmasks. 
Cosmic ray rejection was performed with the dual outlier and multi-frame techniques.
The pixel size of the mosaic was set to be the same as the input cBCD frames ($1''.22 \times 1''.22$).
For $3.6~\rm \mu m$ observations with this pixel scale, 
the photometric zeropoint magnitude is $m_{\rm zp} = 17.26 \rm~mag$.
The orientation of the mosaic was set to the average rotation angle of the input cBCD frames. 
%{\bf TBD: not n-e oriented or re-sampled because problems with 2d PSF. }
Individual cBCD frames were combined together into a single mosaic with the default linear interpolation algorithm.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/m49nooverlap.eps}
\includegraphics[width=0.49\columnwidth]{images/m49overlap.eps}
\caption{Example of the \emph{overlap} correction. 
The image mosaic of the galaxy M49 was obtained by co-adding frames coming from 8 different AORs.
The evident patchiness (left image) was removed (right image) using the \emph{overlap} module.}
\label{fig:overlap}
\end{center}
\end{figure}

@@

\subsubsection{Additional aestethic corrections}
\label{sec:aesth}
The image mosaics of 4 galaxies (NGC 0821, NGC 2974, NGC 4291, NGC 4459) were found to be affected 
by bright, highly saturated stars lying close to the target galaxies.
These stars were modeled and subtracted using the software Galfit \citep{peng2010} 
and the extended IRAC Point Response Function (PRF) image at $3.6~\rm \mu m$.
This helped remove the extended wings and spikes of the saturated stars 
(see Figure \ref{fig:aesth} for an example).

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n4459brightstar.eps}
\includegraphics[width=0.49\columnwidth]{images/n4459nobrightstar.eps}
\caption{Example of aestethic correction.
The images show the mosaic of the galaxy NGC 4459 before (left) and after (right) the partial removal 
of a bright saturated star.}
\label{fig:aesth}
\end{center}
\end{figure}

\subsubsection{Image masking}
Galactic stars and any other objects different from the target galaxy 
were masked through a two-step procedure.
First, we created an initial mask using the IRAF task 
{\tt objmasks} that identifies objects by threshold sigma detection.
Then, we refined each mask by hand, using the software 
SAOImage DS9\footnote{SAOImage DS9 development has been made possible by funding 
from the Chandra X-ray Science Center (CXC) 
and the High Energy Astrophysics Science Archive Center (HEASARC).} 
in conjunction with the IRAF task 
{\tt mskregions}. %\footnote{{\tt mskregions} is part of the {\tt proto} package.}.
We identified and carefully masked not only contaminating sources located in the field of the image mosaic,
but also objects overlapping with the target galaxy, such as foreground stars, background galaxies, 
globular clusters or red giant stars.

\subsubsection{1D PSF}
A universal, average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected galaxy radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
%We employed both a Gaussian and a Moffat \citep{moffat1969} profile. 
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained %$FWHM = 2''.03$ for the Gaussian function,
$(\alpha, \beta) = (2''.38, 4.39)$ %for the Moffat function
(see Appendix \ref{sec:app1} for the analytical expressions of the Moffat function).

\subsubsection{2D PSF}
The IRAC support team provides users with a two-dimensional instrument Point Response Function (PRF) at $3.6~\rm \mu m$.
However, while this helped remove the extended wings of saturated stars (see Section \ref{sec:aesth}), 
we found this PRF to be inadequate for the purposes of our modelling.
In fact, the $FWHM$ of the IRAC instrument PRF ($\sim 1''.8$), as measured by the IRAF task {\tt imexamine}, 
is systematically smaller than the average $FWHM$ of ``real'' stars ($\sim 2''.0$). 
Figure \ref{fig:psf} illustrates this issue.
We also tested the IRAC PRF by providing it as the input Point Spread Function (PSF) for Galfit 
and fitting a number of stars in different image mosaics.
A visual inspection of the fit residuals confirmed that the IRAC instrument PRF is narrower than ``real'' point sources.
For this reason, we constructed our 2D PSF according to the following method 
(as directed by C. Peng, private communication).\\
We provided the IRAC instrument PRF as the input PSF for Galfit 
and simultaneously fit 7 bright stars (belonging to different mosaics), 
modeling the stars with Moffat profiles 
and constraining all the profiles to have the same $(\alpha, \beta)$, position angle and axis ratio.
The 2D PSF image was then obtained by taking the best fit Moffat model -- the same best-fit model for all 7 stars, by construction -- 
and convolving it with the IRAC instrument PRF.
The advantage of this method is to obtain a 2D PSF that is wider than the instrument PRF, 
but maintains the asymmetric features of the instrument PRF (e.g.~wings and spikes).
%This procedure was repeated using a Moffat profile in place of the Gaussian profile.
We then tested this 2D PSF 
on a number of stars (these stars were different from the 7 stars employed to build the 2D PSF image)
and verified that it correctly reproduces the shape of ``real'' point sources.

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth, trim = 220 30 20 20, clip=True]{images/psf.eps}
%\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
%\includegraphics[width=1\columnwidth]{images/PRF_IRACch1_129_129_cut.eps}
\caption{Normalized flux versus radial distance 
from the image centroid of an observed point source (bottom panel) 
and of the IRAC instrument Point Response Function (PRF, top panel). 
The normalized flux is given in arbitrary units, 
and the radial distance is in units of pixel size of the IRAC detector (1 pixel = $1''.22$).
The blue solid line shows our 1D Moffat PSF model,
which has been normalized to intersect the data point with the largest flux. 
The $FWHM$ of the IRAC PRF is clearly smaller than that of a ``real'' star.
The inserts display the images of the observed point source and the IRAC PRF.}
\label{fig:psf}
\end{center}
\end{figure}

\subsection{Additional data}
\label{sec:adddata}
\subsubsection{Kinematics}
\label{sec:kinem}
A kinematical classification (slow/fast rotator) is available for 34 of our 75 galaxies 
from the ATLAS$^{\rm 3D}$ survey \citep{atlas3dIII-MNRAS} 
and for 3 additional galaxies from \citet{scott2014}.
This classification (Table \ref{tab:sample}, column 7) 
concerns the kinematic properties of galaxies within the spectroscopic instrument's field-of-view, 
but does not contain additional information -- crucial for our analysis -- about kinematic substructures, 
such as embedded disks or kinematically decoupled components, 
which can require separate modeling.
For this reason, we also visually inspected the velocity fields of our galaxies, 
when available from the literature.
Velocity maps were taken from the ATLAS$^{\rm 3D}$ survey for 34 galaxies 
(observed with SAURON by \citealt{krajnovic2011}),
from \citet{scott2014} for 2 galaxies 
(observed with WiFeS)
and from the SLUGGS survey for 12 galaxies 
(observed with DEIMOS by \citealt{arnold2014}).
While the field-of-views of SAURON ($33'' \times 41''$) and WiFeS ($25'' \times 38''$) 
reach to about one galaxy effective radius (for our local galaxies),
observations taken with DEIMOS can probe the galaxy kinematics well beyond two effective radii.

\subsubsection{AGNs and nuclear dust}
The X-ray, UV and optical radiation 
emitted by the the accretion disks of Active Galactic Nuclei (AGNs) can stimulate infrared thermal emission 
from circumnuclear dust, if present. 
This means that if a galaxy hosts an optical AGN \emph{and} a certain amount of nuclear dust,
we may detect some non-stellar nuclear emission at $3.6~\rm \mu m$.
It is therefore important to identify which of our galaxies have both an optical AGN and circumnuclear dust.
To help with this task, we searched NED\footnote{NED is the NASA/IPAC Extragalactic Database.} 
for the individual galaxies and their associated literature.
Unsurprisingly, dusty AGNs were more frequently found in late-type spiral galaxies, 
and modelled by us with either a point source or a PSF-convolved Gaussian.

\subsubsection{S\'ersic/core-S\'ersic classification}
\label{sec:corser}
Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
with partially depleted cores, 
i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
Such deficits were first noted and researched by \cite{kingminkowski1966}.
S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
\citep{dullograham2013cores,rusli2013}.
The majority are thus unresolved in our image mosaics. 
We masked these unresolved cores (identified in high-resolution images, see Table \ref{tab:sample}) by excluding the surface brightness profile 
within 3 PSF's $FWHM$ from the galaxy center.
In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
plus 3 PSF's $FWHM$.
The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
This resulted in us assigning cores to just 2 galaxies using this alternative method when 
no high resolution image was available.
